### 2018-01-22 response_to_referee.txt

     I am sure the authors are aware of the difference between both,
     and should know they don't even agree beyond simple cases: such
     as for normally distributed data. Hence the quote "Because they
     are so afraid of being confused with frequentists, Bayesians
     often call these regions "credible" rather than "confidence""

     Not only seems inappropriate for a scientific paper, but it is
     actually misleading. See for instance The fallacy of placing
     confidence in confidence intervals, Morey et al. 2015
     https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4742505/

     Moreover, such discussion -- Bayesian vs Frequentist -- has far
     deeper roots. See e.g. Probability theory, the logic of science,
     E.T. Jaynes, Cambridge University Press 2003.

Actually, our problem is not with the differences -- they are huge and
real -- it is with the *names*. We agree with the referee that these
two things are importantly and substantially different!  They have
totally different meanings, of course. We have fixed that all up in
the text now, making it clear that these are not the same thing at
ALL. We changed both the footnote (and extended it to make the point)
and also the text that is so footnoted.

@@

     ---------------------------------------------------------------------- 
     Statistics Editor Comments:

     As a didactic presentation, I suggest two additions:

     (a) Add a table listing MCMC approaches so the reader appreciates
     the variety of options available
     (e.g. https://www.rdocumentation.org/packages/LaplacesDemon/versions/16.0.1/topics/LaplacesDemon)

We explicitly consider this out of scope, as we have said both early in
the paper, and in the Advanced-Methods section. We call out to much more
comprehensive reviews of methods, which have these tables and full
descriptions of the methods.

@@

     (b) Discuss how to choose when MCMC sampling and when
     optimization (e.g. EM Algorithm or simplex) is appropriate. The
     former is commonly used for characterizing Bayesian posteriors
     while the latter are commonly used for maximizing likelihoods.

We have added more detail to our optimization comment in the introduction.

### 2018-01-22 mcmc.tex
stats editor

All that said, and adhering to the traditions of the \project{Data
  Analysis Recipes} project\note{Every entry in the \project{Data
    Analysis Recipes} series begins with a rant in which we argue that
  most uses of the methods in question are not appropriate!}, we are
compelled to note at the outset that \MCMC\ is in fact \emph{over-used}.
Because \MCMC\ provably (under assumptions\note{The assumptions include
  things like:  The algorithm is run ``long enough'', where this phrase
  is undefined (since the convergence requirements are set by precision
  requirements on particular integrals), and that the density that is
  being sampled has some connectedness properties:  There aren't distant islands of finite density
  separated by regions of zero (or exceedingly low) density.}, some of which will be discussed) samples the full
posterior pdf in all of parameter space, many investigators use \MCMC\
because (they believe) it will sample \emph{all} of the parameter space
($\pars$-space).
That is, they are using \MCMC\ because they want to
\emph{search the parameter space for good models}.
This is not a good reason to use \MCMC!
Another bad use case is the following:
Because \MCMC\ samples the parameter representatively, it spends most of
its time near very good models; models that (within the confines of
the prior pdf) do a good job of explaining the data.
For this reason, many investigators are using \MCMC\ because it
effectively \emph{optimizes the posterior pdf}, or, for certain
choices of prior pdf, \emph{optimizes the likelihood}.\note{Of course
  a committed Bayesian would argue that any time you are optimizing a
  posterior pdf or optimizing a likelihood, you \emph{should} be
  sampling a posterior pdf.  That is, for some, the fact that when
  someone ``wants'' to optimize, it is actually useful that they
  choose the ``wrong'' tool, because that ``wrong'' tool gives them
  back something far more useful than the output of any optimizer!}
This is another bad reason!

>>>>

All that said, and adhering to the traditions of the \project{Data
  Analysis Recipes} project\note{Every entry in the \project{Data
    Analysis Recipes} series begins with a rant in which we argue that
  most uses of the methods in question are not appropriate!}, we are
compelled to note at the outset that \MCMC\ is in fact \emph{over-used}.
Because \MCMC\ provably (under assumptions\note{The assumptions include
  things like:  The algorithm is run ``long enough'', where this phrase
  is undefined (since the convergence requirements are set by precision
  requirements on particular integrals), and that the density that is
  being sampled has some connectedness properties:  There aren't distant islands of finite density
  separated by regions of zero (or exceedingly low) density.}, some of which will be discussed) samples the full
posterior pdf in all of parameter space, many investigators use \MCMC\
because (they believe) it will sample \emph{all} of the parameter space
($\pars$-space).
That is, they are using \MCMC\ because they want to
\emph{search the parameter space for good models}.
This is not a good reason to use \MCMC!
Another bad use case is the following:
Because \MCMC\ samples the parameter representatively, it spends most of
its time near very good models; models that (within the confines of
the prior pdf) do a good job of explaining the data.
For this reason, many investigators are using \MCMC\ because it
effectively \emph{optimizes the posterior pdf}, or, for certain
choices of prior pdf, \emph{optimizes the likelihood}.\note{Of course
  a committed Bayesian would argue that any time you are optimizing a
  posterior pdf or optimizing a likelihood, you \emph{should} be
  sampling a posterior pdf.  That is, for some, the fact that when
  someone ``wants'' to optimize, it is actually useful that they
  choose the ``wrong'' tool, because that ``wrong'' tool gives them
  back something far more useful than the output of any optimizer!
  However it is true that when the data are extremely informative
  (that is, the posterior is very narrow), there is not much difference
  between optimizing the posterior and sampling it, nor between optimizing
  the likelihood and optimizing the posterior. That is, all inference
  methods sort-of converge as the data become very informative. That can be
  an important point when you are working on a problem where the posterior
  is very narrow.}
This is another bad reason!
